Compositional Certified Resource Bounds\ifshort{\vspace{-1.15cm}}{}

### 2014-11-12 paper/main.tex
pack figure 8

\begin{figure*}
\centering
\begin{tabular}{r|c|c|c|c|c}
%
& t08 (modified t08a) & t19 & t30 & t15 & t13\\
%
\hline
&
\begin{lstlisting}[basicstyle=\tt\scriptsize]
while (y > x) {
  x++; tick(1);
}
while (x > 2) {
  x -= 3; tick(1);
}
\end{lstlisting}
&
\begin{lstlisting}[basicstyle=\tt\scriptsize]
while (i > 100) {
  i--; tick(1) }
i += k+50;
while (i >= 0) {
  i--; tick(1);
}
\end{lstlisting}
&
\begin{lstlisting}[basicstyle=\tt\scriptsize]
while (x > 0) {
  x--;
  t=x, x=y, y=t;
  tick(1);
}
\end{lstlisting}
&
\begin{lstlisting}[basicstyle=\tt\scriptsize]
assert(y >= 0);
while (x > y) {
  x -= y+1;
  for (z=y; z > 0; z--)
    tick(1);
  tick(1);
}
\end{lstlisting}
&
\begin{lstlisting}[basicstyle=\tt\scriptsize]
  while (x > 0) {
    x--;
    if (*) y++;
    else
      while (y > 0) {
        y--; tick(1); }
    tick(1); }
\end{lstlisting}
%
\\
\hline
%
%
%
AAA
  & {\small $1.33|[x,y]| {+} 0.33 |[0,x]|$ }
  & {\small $50 {+} |\inter {-1} i| {+} |\inter 0 k|$ }
  & {\small $|\inter 0 x| {+} |\inter 0 y|$}
  & {\small $|\inter 0 x|$}
  & {\small $2 |\inter 0 x| {+} |\inter 0 y|$}
\\
%
Rank &
{\small $2 {+} y {-} x (?)$ } &
{\small $54+k+i$ } &
{\small ---} &
{\small $2+2x-y$ } &
{\small $0.5{\cdot}y^2 {+} yx +0.5{\cdot}x^2\ldots$} % + 1{-}0.5{\cdot}y){-}0.5{\cdot}x $}
\\
%
LOOPUS &
{\small
  \begin{tabular}{c}
    $\max(0, x{-}2)$\\ $+ 2\max(0, y {-} x)$
  \end{tabular}
} &
{\small
  \begin{tabular}{c}
    $\max(0, i{-}100)$ \\
    $+ \max(0, k {+} i {+} 51)$
  \end{tabular}
 } &
{\small ---}% $1 + \max(x, y)$ (???)
&
{\small ---}
&
{\small $2\max(x, 0) {+} \max(y, 0)$}
\end{tabular}
\vspace{.1cm}
\caption{ Comparison of resource bounds derived by different tools on
  several examples with linear bounds.  AAA stands for our automatic
  amortized analysis for Clight.  The output of Rank has been manually
  simplified to fit the table.  }
\label{fig:compar}
\end{figure*}

>>>>

\begin{figure*}
\centering
\begin{tabular}{r|c|c|c|c|c}
%
& t08 (modified t08a) & t19 & t30 & t15 & t13\\
%
\hline
&
\begin{lstlisting}[basicstyle=\tt\scriptsize]
while (y>x) {
  x++; tick(1);
}
while (x>2) {
  x -= 3; tick(1);
}
\end{lstlisting}
&
\begin{lstlisting}[basicstyle=\tt\scriptsize]
while (i>100) {
  i--; tick(1) }
i += k+50;
while (i>=0) {
  i--; tick(1);
}
\end{lstlisting}
&
\begin{lstlisting}[basicstyle=\tt\scriptsize]
while (x>0) {
  x--;
  t=x, x=y, y=t;
  tick(1);
}
\end{lstlisting}
&
\begin{lstlisting}[basicstyle=\tt\scriptsize]
assert(y>=0);
while (x > y) {
  x -= y+1;
  for (z=y; z>0; z--)
    tick(1);
  tick(1);
}
\end{lstlisting}
&
\begin{lstlisting}[basicstyle=\tt\scriptsize]
  while (x>0) {
    x--;
    if (*) y++;
    else
      while (y>0)
        y--, tick(1);
    tick(1); }
\end{lstlisting}
%
\\
\hline
%
%
%
{\footnotesize \toolname}
  & {\small $1.33|[x,y]| {+} 0.33 |[0,x]|$ }
  & {\small $50 {+} |\inter {-1} i| {+} |\inter 0 k|$ }
  & {\small $|\inter 0 x| {+} |\inter 0 y|$}
  & {\small $|\inter 0 x|$}
  & {\small $2 |\inter 0 x| {+} |\inter 0 y|$}
\\
%
{\footnotesize Rank}
  & {\small $2 {+} y {-} x (?)$ }
  & {\small $54+k+i$ }
  & {\small ---}
  & {\small $2+2x-y$ }
  & {\small $0.5{\cdot}y^2 {+} yx \ldots$}
           % +0.5{\cdot}x^2\ldots$} % + 1{-}0.5{\cdot}y){-}0.5{\cdot}x $}
\\
%
{\footnotesize LOOPUS}
&
{\small
  \begin{tabular}{c}
    $\max(0, x{-}2)$\\ $+ 2\max(0, y {-} x)$
  \end{tabular}
}
&
{\small
  \begin{tabular}{c}
    $\max(0, i{-}100)$ \\
    $+ \max(0, k {+} i {+} 51)$
  \end{tabular}
}
&
{\small ---}% $1 + \max(x, y)$ (???)
&
{\small ---}
&
{\small \begin{tabular}{c}
           $2\max(x, 0)$ \\
           $+ \max(y, 0)$
        \end{tabular}}
\end{tabular}
\vspace{.1cm}
\caption{ Comparison of resource bounds derived by different tools on
  several examples with linear bounds.  AAA stands for our automatic
  amortized analysis for Clight.  The output of Rank has been manually
  simplified to fit the table.  }
\label{fig:compar}
\end{figure*}
